Miniproject - Elliptic Curves

### 2022-03-31 Elliptic Curves/submission.tex
Added introduction and conclusion to elliptic curves

@@

>>>>

\section*{Introduction}
In this Miniproject, we study several phenomena that can occur when computing the group of rational points $E(\Q)$ of an Elliptic Curve $E$.
In particular, we look at the two most important tools for studying this group that were introduced in the lecture. 
Firstly, this is the fact that the reduction modulo a prime is injective on torsion points, and thus provides a good way to find the torsion part of $E(\Q)$.
The second tool is the 2-descent method, which can be used to find the rank (i.e. the dimension of the free part of $E(\Q)$).

When applying these methods, there are some exceptional (and therefore interesting) situations that can occur.
We want to present some of these phenomena by giving examples, and analyze what conditions must be satisfied for them to occur.

@@

\section*{Conclusion}
In this work, we have seen a lot of examples of Elliptic Curves with interesting behavior.
The first question dealt with cases in which there are (almost) no points with coordinates in $\Z_p$ on the curve, for certain $p$.
By Hensel's Lemma, this is very closely related to the $\F_p$-rational points of the reduction of $E$ modulo $p$, and we have seen that this only exhibits special behavior for small primes.

In the second question, we continued to study the reduction modulo $p$ and looked for situations where the group of $\F_p$ rational points in the reduction is strictly larger than the torsion group of $E(\Q)$.
These cases are interesting, as they complicate the computation of the torsion group using the standard techniques.

The third question continued to deal with rational torsion points, but now we wanted to find Elliptic Curves with torsion points of specified order.
As it turns out, in some cases we have found a family of defining equations that completely characterize these Elliptic Curves.
Together, we note that when it comes to the torsion group, we find a lot of nice connections and can make definite statements about its structure.
All in all, we understand the torsion part of $E(\Q)$ quite well.

The last question however deals with the free part of $E(\Q)$ (in particular the rank of $E$), which is much more mysterious.
Our main obstacle is that the naive 2-descent method from the lecture only works in a few cases, and in other cases, it is extremely difficult to compute the rank.
We also could not find nice characterizations of whenever the method works.
However, working around this obstacle, we still could find some interesting examples and find their rank.
Furthermore, we present a sharp bound on the rank, which only depends on the coefficients of the Elliptic Curve in a simple way.

Of course, when it comes to the rank, there are still a lot of open questions, and we just touched the topic on the surface.
For example, I would find it interesting to study whether the fact that isogenies preserve the rank allows to prove more statements or compute the rank in more cases.
Finally, this line of thought also leads into current research, and is even connected to one of the Millenium Problems, namely the Birch and Swinnerton-Dyer Conjecture.
